Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-03 metrics.tex
Editing metrics

To complement our study, we consider the goodput defined as the ratio
of the useful delivered information at the application layer and the total
delivery time. We focus on the goodput considering only the coding process,
i.e. we assume that the application data has been properly
generated before encoding and also correctly post-processed after decoding.
The goodput is a measure for the effective processing speed since it
excludes protocol overhead but considers process

\subsection{Energy Costs}
\subsubsection{Average Consumption}
\subsubsection{Per-Bit Consumption}

>>>>

To complement our study, we consider the goodput defined as the ratio
of the useful delivered information at the application layer and the total
delivery time. We focus on the goodput considering only the coding process,
i.e. we assume that the application data has been properly
generated before encoding and also correctly post-processed after decoding.
The goodput is a measure for the effective processing speed since it
excludes protocol overhead but considers all delays related with
algorithmic procedures, field operations, hardware processing,
multicore coordination (where it applies), etc. Moreover, encoding
and decoding goodput permits to observe if coding is a system-block
that limits the end-to-end performance. For example, a low goodput
would affect the \ac{QoE} of delay-densitive applications for the
end user. Use cases of the

\subsection{Energy Consumption}
\subsubsection{Average }
\subsubsection{Per-Bit}
